---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5, pillar.bold = TRUE)
```

## Overview
A collection of all the user-defined functions I commonly use, including both the well-documented functions from my other repos and any work-in-progress functions I'm currently developing. Most of the less experimental functions included in this package can be found in
[vary](https://github.com/ulchc/vary) 

## Installation

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ulchc/ulchr")
```

## Usage

After installation from GitHub, you can load it with:
```{r, eval=TRUE}
library(ulchr)
```

```{r, include=FALSE}
library(tidyr)
library(dplyr)

data <- tibble(
  ID     = "5.1.0",
  Code   = "222",
  Name   = "Book",
  Day    = "Friday",
  Month  = "APR",
  Amount = "19.00"
)

messy_data <- tibble(
  `Amount $`           = "20.00",
  `Month (MMM) `       = "MAY",
  `Day of \n the week` = "Saturday",
  `Product\nName`      = "Notebook",
   Barcode             = "223",
  `ID #`               = "5.1.1"
)

color_phrases <- c(
  "The sunrise was 'yellovv'",
  "There were 'purp/e' flowers",
  "The fruit was 'orang e'"
)

colors_list <- c(
  "Red",
  "Blue",
  "Green",
  "Yellow",
  "Violet",
  "Purple",
  "Orange"
)

set.seed(1)
mismatched <- tidyr::table2
n_rows <- sample(nrow(mismatched), 5)
mismatched[n_rows, 1] <- table2[n_rows, 3]
mismatched[n_rows, 3] <- table2[n_rows, 1]
```

Using fuzzy_rename() when it is known that the underlying data between two sources is equivalent 
```{r}
# The attributes of data and messy_data are the same, but naming conventions between the sources differ
```

```{r}
data
messy_data
```

```{r}
names(data) %in% names(messy_data)

# No names are compatible between sources
```

```{r}
names(data) %in% names(fuzzy_rename(messy_data, names(data)))

# fuzzy_rename() will match names and print out the changes
```

Automatically match, reorder, and combine without making manual adjustments
```{r}
messy_data %>%
  fuzzy_rename(data) %>%
  select(names(data)) %>%
  rbind(data)
```

Using fuzzy_match() to categorize and handle spelling mistakes from OCR text
```{r}
colors_list
```
```{r}
color_phrases
```

```{r}
colors_mentioned <- fuzzy_match(color_phrases, colors_list)

# A message will indicate when there is a large string distance between fuzzy matches
```
```{r}
writeLines(paste0("The colors mentioned were: ", paste0(colors_mentioned, collapse = ", ")))
```

Use which_rows() to filter data with mismatched columns
```{r}
# Mismatched columns: country < -- > type
```
```{r}
mismatched
```

```{r}
row_index <-
  which_rows(
    mismatched,
    contain_strings = c("CASES", "2000"),
    all_strings = TRUE,
    case_sensitive = FALSE,
    flatten = TRUE
  )
```

```{r}
# Using which_rows() to filter data prior to resolving mismatched attributes
```
```{r}
mismatched[row_index, ]
```

```{r}
# dplyr::filter is, of course, not designed to work under such conditions and would only return 2/3 of the rows 
```
```{r}
mismatched %>% filter(type == "cases" & year == 2000)
```

## R Documentation

Use ?vary in R to view a linked list of all functions

